---
title: "CS Salary"
author: "Harrison Grogan"
date: "5/1/2021"
output:
  pdf_document: default
  html_document: default
---

```{r, warning=FALSE, include=FALSE}
library(tidyr)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(data.table)
library(corrgram)
library(gridExtra) 
library(knitr)
library(heplots)
library(GGally)
library(reshape)
library(rsconnect)
library(shiny)
library(rmarkdown)
```

## ABSTRACT
## My project is about Computer Science Salaries and what the difference is into how much you are paid. This is important because it is never a bad idea to educate yourself on how certain aspects of your line of work are decided. I saw someone answer someone else's question about whether age has anything to do with people losing their jobs in the Computer Science field. The person went on to explain that a lot of Computer Science workers lose their job around 50, not due to ageism, but due to people just slacking off and not keeping up with their programming skills. My research question is: Is there any link to how someone is paid when it comes to their age and gender? I got my data from a website called Data USA. I analyzed my data through and I found that age has little to do with whether or not someone keeps their job. 


## Introduction
## My name is Harrison Grogan and I did my R project over the differences in Salary when it comes to age. I want to find out if there are true differences in pay.

## Literature Review
## Another post that I read through talked about how people in the Computer Science field are not fired based solely on their age, but rather their skill wearing down and slacking off. One aspect that I am planning to address in the future is how your location effects your salary. My research question is: Is there any link to how someone is paid when it comes to their age?

## Data
## The application that I used to download the data is called ParseHub. ParseHub is a really good application when it comes to data mining. It's easy to use and very fast. The way to use ParseHub is by putting the link to the page/website you want to data mine from and then you select the data, but you don't select the data one-by-one, you select two pieces of data and it auto fills the rest for you, then when you're ready you can download it into a csv file and transfer it to R.

## Methodology
## After I read my csv file into R, I then proceed to check the contents of the file and noticed that there were a few columns there that I did not need, so I began by taking the columns out using the subset function with -c(...). Then I proceeded to analyze the data using scatterplot graphs and some bar charts, but the bar charts weren't very helpful so I stuck with the scatterplots. I used the lm() function to create a linear model and look over the data there. I also used the step function to create a step model too. 

## Results
## As mentioned earlier in Abstact, the results that I found weren't too shocking after the article that I read. Age doesn't have much to do with getting salary decreased or being fired, it's more just people getting old and being sick of working in the Computer Science field.

## Implications
## I did not find anyone that would be a true researcher in this topic. 

## Conclusion
## What I have achieved is showing that age does not have a factor on people losing their jobs. If you keep your skills sharpened and try not to slack off, then you will probably have a long career in Computer Science. 

## References
## Walsh B T. (2015).  Is it true that computer science people only have good jobs till the age of 35-40? Quora. https://www.quora.com/Is-it-true-that-computer-science-people-only-have-good-jobs-till-the-age-of-35-40

##N/A. (2019). Computer Science. Data USA. https://datausa.io/profile/cip/computer-science-110701#demographics

##Williams H. (March 29, 2019). Ageism in tech: the not-so-invisible age limit developers face. https://bdtechtalks.com/2019/03/29/ageism-in-tech-age-limit-software-developers-face/https://bdtechtalks.com/2019/03/29/ageism-in-tech-age-limit-software-developers-face/


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
salaryAge <- read_csv("C:/Users/groga/OneDrive/Desktop/Workforce_Age.csv")
salaryAge

salaryAge_df = subset(salaryAge, select = -c(`ID Age`, `ID Year`, `Workforce Status`, `Record Count`, CIP2, `ID CIP2`, share, `Total Population MOE Appx`, `Average Wage Appx MOE`, `ID Workforce Status`, Year))
salaryAge_df
```


```{r}
lapply(salaryAge_df, FUN=summary)
```


```{r}
ggplot(salaryAge_df, aes(x = Age, y = `Average Wage`)) + geom_point() + stat_smooth()
```


```{r}
lin <- lm(`Average Wage` ~ Age ,salaryAge_df)
summary(lin)
```


```{r}
predicted_salary = 605.4*22 + 61027
predicted_salary
```






